---
title: "Data Organization"
author: "Emma Jones"
date: "12/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(pool)
library(config)
library(sf)
library(readxl)

```

# R version

This application is built in R 3.6.2 to comply with geospatial dependencies on the R server.


## Background

This document walks users through all data acquisition and manipulation necessary for updating datasets beneath the WQM Data Query Tool.

### ODS Connectivity

Before beginning, make sure you have access to ODS production environment variables necessary to build the application.

```{r ODS connectivity}
# Server connection things
conn <- config::get("connectionSettings") # get configuration settings

## For testing: connect to ODS production
pool <- dbPool(
  drv = odbc::odbc(),
  Driver = "ODBC Driver 11 for SQL Server",#"SQL Server Native Client 11.0", 
  Server= "DEQ-SQLODS-PROD,50000",
  dbname = "ODS",
  trusted_connection = "yes"
)

# Fpr deployment on the R server: Set up pool connection to production environment
#pool <- dbPool(
#  drv = odbc::odbc(),
#  Driver = "SQLServer",   # note the LACK OF space between SQL and Server ( how RStudio named driver)
#  # Production Environment
#  Server= "DEQ-SQLODS-PROD,50000",
#  dbname = "ODS",
#  UID = conn$UID_prod, 
#  PWD = conn$PWD_prod,
#  #UID = Sys.getenv("userid_production"), # need to change in Connect {vars}
#  #PWD = Sys.getenv("pwd_production")   # need to change in Connect {vars}
#  # Test environment
#  #Server= "WSQ04151,50000",
#  #dbname = "ODS_test",
#  #UID = Sys.getenv("userid"),  # need to change in Connect {vars}
#  #PWD = Sys.getenv("pwd"),  # need to change in Connect {vars}
#  trusted_connection = "yes"
#)
```

### ProbMon Estimates

This version of the application is the first to include basin-specific estimates (opposed to just superbasin) as the 2020IR officially published these data and thus they are available for use in other applications.

```{r prob Estimates}
probCDF <- read_csv('C:/HardDriveBackup/R/GitHub/ProbMon-Integrated-Reports/2020ProbChapter/processedData/allCDF.csv')

# add unit information
unitData <- read_csv('data/probIndicatorUnits.csv')

probCDF <- left_join(probCDF, unitData, by = 'Indicator')
# save to RDS locally for better data manipulation experience
# drop first blank row
saveRDS(probCDF[2:nrow(probCDF),], 'data/IR2020probMonCDFestimates.RDS')
```

```{r}
LRBS <- read_excel('C:/HardDriveBackup/TMDLsummary_2021-05-25.xlsx')

pin(LRBS, description = 'TMDL Summary LRBS results, last run 02/25/21.', board = 'rsconnect')
```


